\plaintitle

### 2017-01-11 drafts/labor/discussion.tex
release candidate 2

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}.
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete the task, decomposition seems a poor choice.

@@

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }

>>>>

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}. % Chinmay wanted me to specifically call out that this is from chapter 6. Is that necessary...?
% \ali{Chinmay: <suggestion to look at \cite{stigler1962information} and friction> --- not sure if worth getting into.}
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete the task, decomposition seems a poor choice.

@@

We should also take a moment to explore opportunity to discuss the ethics of on--demand labor,
as \citeauthor{williamson2016} does~\cite{williamson2016}.
% with a set of tools and perspectives that took shape only after piecework's nascent years.
The literature on the history of piecework does not
frame the question as \textit{whether piecework is inherently ethical or unethical},
instead asking what conditions render it exploitative.
The literature we have brought to bear suggests that exploitation occurs when
conditions harm workers directly or indirectly, such as
in sweatshops and agricultural work with pesticides, or where
employers \textit{systematically} underpay or overwork laborers by contemporary standards.

The question then is
whether given socio--technical infrastructures % like Mechanical Turk (AMT)
% and other marketplaces
similarly harm, underpay, or overwork workers.
As an example, Amazon Mechanical Turk itself does not directly require any rate of payment for work,
but its design encourages employers to engage in exploitative behavior:
the use of piecework remuneration, for example, workers' task search time poorly;
task design interfaces undeniably frame
workers as unreliable by recommending
replication with multiple workers rather than
trusting and paying individual workers more.

Piecework also has lessons for many other research questions in crowdsourcing.
For example, future work could more deeply explore the evolution of
scientific management as it relates to
crowdsourcing optimization methods,
quality control methods between the two eras, and
a further analysis of incentive structures.

% This is

% \ali{
% Discussions from Slack:

% Chinmay: I think the most provocative claim is ``The history of piecework suggests that the utopian and dystopian outcomes will both occur, in different parts of the world and to different people.''\\
% seems contrary to the idea that marketplaces are global\\
% I would also like some more thought into the Research Agenda section\\

% Ali: so the dystopian and utopian claim is partly influenced by the fact that piecework seemed to affect some industries differently than others\\

% Chinmay: ah ok\\
% i think you could claim the same about online piecework\\
% differnt industries\\

% Ali: garment-makers were pretty thoroughly marginalized, but industrial metalwork led to this whole WWII phenomenon with expert training\\
% mmmm\\
% but now it's not just about the industry, but about the design of the labor market\\
% we can influence the ``architecture'' in a way that we couldn't before\\
% this is all lessig and stuff\\

% Chinmay: oh\\
% i understand\\
% hmm something there\\
% might poke more :)

% \dotfill

% Chinmay> i wish you had a little more criticality in taylorism but I'm a downer :)

% Ali> actually a reviewer wanted more on taylorism but i was afraid that we just didn't have the space to really give anyone into taylorism what they want

% Chinmay> essentially that would be a great place to talk about how those three questions you mentioned interact

% Ali> oh
% that might be worth fitting in
% i mean we inexplicably got it down to 9.5 pages or so
% or 9.75
% we were over for like 99\% of the drafting and then inexplicably something just imploded and we got like half a page
% so yeah i'll try and write something giving taylorism more space and using that to talk about the confluence of these three questions
% }
